---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![Travis-CI Build Status](https://travis-ci.org/r-gris/rlas.svg?branch=master)](https://travis-ci.org/r-gris/rlas)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/r-gris/rlas?branch=master&svg=true)](https://ci.appveyor.com/project/r-gris/rlas)
[![Coverage Status](https://img.shields.io/codecov/c/github/r-gris/rlas/master.svg)](https://codecov.io/github/r-gris/rlas?branch=master)

  
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## Read "LAS" format, raw LiDAR point cloud format

Read the raw point records into a data frame. 


```{r,eval=FALSE}
library(rlas)
x <- lasfile("somefile.las")


```

## TODO 

Not all the specification is supported, and there are better tools for LAS data - just not available in R yet. 

* put all file contents into a `spbabel::map_table`-like structure
* put plot methods into 'r-gris/rangl'
* support RGB LAS
* extract all bit type columns




## Installation

```{r,eval=FALSE}
devtools::install_github("r-gris/rlas")
```



Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms. 